Telemetry Module for Solar Vehicle

### 2021-06-17 documentation/FinalPaper/paper.tex

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/EnhancedShockburst.png}
    \caption{The Enhanced Shockburst$^\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}

@@

As a specific RTOS, we chose ChibiOS \cite{chibios}, since it supported both the Teensy 3.6 and 4.0 and since it attempts to keep the memory footprint of the real time kernel as small as possible.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/MessageTypes.pdf}
    \caption{The different message types used in the telemetry system.\todo{delete uint16\_t part in fig and make cmd to broadcast can}}
    \label{fig:messageTypes}
\end{figure}

@@

As an extra feature not included in our original specification, we have made an encryption protocol for our telemetry module. The encryption is based on the RSA algorithm, which essentially generates an encryption key based on the modulus and totient function of two prime numbers. The pairings of prime numbers suited for the encryption protocol can be seen below in Table \ref{}. When a message is encrypted, each of the 16 bytes is extended to a 16-bit unsigned integer to avoid overflow problems. Once transmitted to the receiving node, the message is then decrypted and converted back to unsigned 8-bit type. This essentially doubles the size of the data payloads being sent in our RF transmission, which is the downside of our encryption solution.

@@

\section{\todo{Final product}}
\subsection{Solar Car}
% threads 
\subsection{Support Vehicle}
% threads
\subsection{\todo{Graphical User Interface}}
% GUI

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/EnhancedShockburst.pdf}
    \caption{The Enhanced Shockburst$^\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}

@@

As a specific RTOS, we chose ChibiOS \cite{chibios}, since it is supported both the Teensy 3.6 and 4.0 and since it attempts to keep the memory footprint of the real time kernel as small as possible.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/MessageTypes.pdf}
    \caption{The different message types used in the telemetry system.}
    \label{fig:messageTypes}
\end{figure}

@@

As an extra feature not included in our original specification, we have made an encryption protocol for our telemetry module. The encryption is based on the RSA algorithm, which essentially generates an encryption key based on the modulus and totient function of two prime numbers. The pairings of prime numbers suited for the encryption protocol can be seen below in Table \ref{fig:prime_tabel}. When a message is encrypted, each of the 16 bytes is extended to a 16-bit unsigned integer to avoid overflow problems. Once transmitted to the receiving node, the message is then decrypted and converted back to unsigned 8-bit type. This essentially doubles the size of the data payloads being sent in our RF transmission, which is the downside of our encryption solution.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/prime_tabel.pdf}
    \caption{Valid combinations of prime numbers, marked by OOOOOO}
    \label{fig:prime_tabel}
\end{figure}

@@

\section{\todo{Final product}}
\subsection{Solar Car}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/SCU_CircuitDiagram.pdf}
    \caption{The circuit diagram for the SCU.}
    \label{fig:SCU_circuit}
\end{figure}
% threads 
\subsection{Support Vehicle}
% threads
\subsection{\todo{Graphical User Interface}}
% GUI
